Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-09 manuscript.tex
fixed up section 4

\subsection{Delay Response}
\label{sec:delayspec}
Need to include initial 60 at 60 and Nithya etc etc etc

\subsection{Sensitivity Optimization}
\label{sec:cost}
As an instrument to characterize the power spectrum over the evolution of the EoR, the specification on sensitivity is to make at least a nominal detection over the redshift region of support, or $z$=6-13, along with a very robust detection at the peak.  As seen in Fig. \ref{fig:Sensitivities} and Table \ref{tab:signif}, an array comprising 320 14-m core antennas (note, labelled HERA-350, which includes the outriggers) has sensitivity to a
fiducial reionization model across that redshift range.  We therefore adopt the delay-spectrum power spectrum sensitivity of 320 14-m close-packed antennas as the minimum sensitivity needed.  
For this sensitivity, the number of elements needed for a given diameter is
\begin{equation}
\label{eq:ND}
N_{\text core} = (320*14)/D
\end{equation}
where $N_{\text core}$ and $D$ are the number of antennas in the core and their diameter respectively.  Note that the linear number-diameter dependence was derived by running multiple sensitivity codes ({\em e.g.} Pober) over a range of values for the HERA configuration for wavenumbers greater than 0.15.  This dependency differs from \cite{2013ExA....36..235M} and analytical expressions, mostly likely due to the assumed configuration.
Optimization is 
therefore done for this sensitivity against cost for various diameters and total element numbers, while trying to minimize multiple reflections on long delays.  Figure \ref{fig:costfig} summarizes this optimization, which
is discussed below.

To determine the optimal diameter, full system costings were done on a range of diameter sizes from 5m - 25m, with the total number set by Eq. \ref{eq:ND}.  This included the full system, except the post-processing (that is, everything after the archived correlator output).  
Figure \ref{fig:costfig} shows the resulting normalized system cost/performance-curve as the horizontal shading relative to the canonical HERA design 
which becomes very flat (colored purple) for diameters greater between about 12 and15 m, which is consistent with the chosen value of 14 meters based on other system considerations.

OTHER LINES IN FIG 12.

\begin{figure}[t]
\centerline{
\includegraphics[width=0.6\textwidth]{plots/costfig.pdf} 
}
\caption{\small The background coloring with colorbar shows the relative cost/performance at a fixed performance as a function of element diameter.  Costing model for a fixed sensitivity system as a function of diameter (thick blue line and left axis) as well as the round-trip delay for 1,2 and 3 feed-vertex trips (dashed red lines and right axis).  The 60 ns spec is indicated by the horizontal dash line, and the two-trip intersection at about 14-meter is the vertical dashed line.  SEE TEXT...
\label{fig:costfig}}
\end{figure}

>>>>

\subsection{Delay Response}
\label{sec:delayspec}
Early analysis \citep{elementmemo} indicated that to trace the EoR over a wide range of redshift, internal reflections should be attenuated by about 60 dB from the initial incoming wave by about 60 ns, or a VSWR $<$ 1.002 for frequencies $<$ 17 MHz.  This provided the basis for the initial design of the element.    For the contemplated feeds for a primary focus antenna, it was found that a focal length/diameter radio ($f/D$ of approximately 0.32 was optimal \citep{elementmemo}.  We may therefore estimate the attenuation as a function of delay and diameter and assign this a ``cost function''.  The vertical axis of Fig. \ref{fig:costfig} shows a very steep cost function at 60 ns.  The curves labelled `1', `2' and `3' are the round-trip travel time for 1, 2 and 3 reflections.

To get 60 dB at 60 ns we may interpret those lines in one of two ways:  (1) set the spec on how much attentuation per reflection is needed and (2) at a fixed attenuation/reflection, what diameter we need.  For 1 round-trip, for the assumed $f/D$ over the diameters of interest, all delays are less than 60 ns, so it provides no constraint.  For
3 round-trips, all diameters exceed 60 ns, so the attenuation should be less than 60 dB for that path-length.  The case for 2 round-trips provides a constraint on attenuation and diameter, which is discussed at length in \cite{elementmemo}.
To estimate, it was assumed that the main reflection time constant was due to the standing waves between the feed and vertex of the parabola and that each reflection redirected about -15 dB of the total power in each reflection for additional standing wave power, which leads to a diameter of about 14m.

As a key specification, this has been a focus of study with our prototypes and a series of papers based on analysis and measurements have been produced to provide much more rigor than this simple early analysis \citep{nithya, ewall-wice, patra}.  The simple specification set above more appropriately becomes a series of curves for attenuation and delay at different wavenumbers for realistic foreground models.  Fig \ref{fig:nithadelay} taken from \cite{nitha} shows the results at $k$ = 0.2 $h$/Mpc for the adopted design.  The analysis shows that for $k>0.15 h/$Mpc, HERA should be able to detect the EoR.  The analysis also shows which baselines produce the best information.

\subsection{Sensitivity Optimization}
\label{sec:cost}
As an instrument to characterize the power spectrum over the evolution of the EoR, the specification on sensitivity is to make at least a nominal detection over the redshift region of support, or $z$=6-13, along with a very robust detection at the peak.  As seen in Fig. \ref{fig:Sensitivities} and Table \ref{tab:signif}, an array comprising 320 14-m core antennas (note, labelled HERA-350, which includes the outriggers) has sensitivity to a
fiducial reionization model across that redshift range.  We therefore adopt the delay-spectrum power spectrum sensitivity of 320 14-m close-packed antennas as the minimum sensitivity needed.  
For this sensitivity, the number of elements needed for a given diameter is
\begin{equation}
\label{eq:ND}
N_{\text core} = (320*14)/D
\end{equation}
where $N_{\text core}$ and $D$ are the number of antennas in the core and their diameter respectively.  Note that the linear number-diameter dependence was derived by running multiple sensitivity codes ({\em e.g.} Pober) over a range of values for the HERA configuration for wavenumbers greater than 0.15.  This dependency differs from \cite{2013ExA....36..235M} and analytical expressions, mostly likely due to the assumed configuration.
Optimization is 
therefore done for this sensitivity against cost for various diameters and total element numbers, while trying to minimize multiple reflections on long delays.

The cost function in Fig. \ref{fig:costfig} is shown as the colored background and color bar, with the delay-spec vertically and the cost at a fixed sensitivity horizontally. 
To determine the optimal diameter, full system costings were done on a range of diameter sizes from 5m - 25m, with the total number set by Eq. \ref{eq:ND}.  This included the full system, except the post-processing (that is, everything after the archived correlator output).  
The resulting normalized system cost/performance-curve  becomes very flat (colored purple) for diameters greater between about 12 and15 m, which is consistent with the chosen value of 14 meters based on other system considerations.

\begin{figure}[t]
\centerline{
\includegraphics[width=0.6\textwidth]{plots/costfig.pdf} 
}
\caption{\small The background coloring with colorbar shows the relative cost/performance for delay and cost at a fixed performance as a function of element diameter.  See text and \cite{elementmemo} for details.  A diameter of 14-m (vertical dashed line) is near the cost minimum and consistent with assumption for the delay specification.
\label{fig:costfig}}
\end{figure}
